---
title: "Population data from OFS"
author: "Duc-Quang Nguyen"
date: "08 06 2016"
output: html_document
---

## Description

The procedure to get the latest commune population data from OFS and match if with my available geo data.
Commune portraits have older population data, swiMap::loadCommunesCHdata that is why this was done

* Population data extracted from [stat-tab](https://www.pxweb.bfs.admin.ch/Selection.aspx?px_language=fr&px_db=px-x-0102010000_101&px_tableid=px-x-0102010000_101\px-x-0102010000_101.px&px_type=PX) 
* selected:
   * year 2014
   * Canton (-) / District (>>) / Commune  -> EVERYTHING
   * Type de population -> EVERYTHING
* saved in data/px-x-0102010000_101.csv

```{r map data, message = F}
library(dplyr)
data.read <- read.table("data/px-x-0102010000_101.csv", 
  skip = 1, sep = "\t", header = T, encoding = "latin1")

data <- data.read %>% select(-Année) %>% 
  rename(loc = `Canton.......District........Commune.........`) %>%
  group_by(loc) %>% summarise(pop = sum(`Population.résidante.permanente.et.non.permanente`)) %>%
  ungroup()

# get only municipalities! (starting with ......)
data <- data[grepl("......", data$loc, fixed = T),]
data$loc <- gsub("......", "", as.character(data$loc), fixed = T)
data$id <- substr(data$loc, 1, 4)
data$idn <- as.numeric(data$id)
data$loc <- gsub("^\\d{4} ", "", data$loc)

```

```{r map data, message = F}
library(swiMap)
require(rgdal)
require(rgeos)
require(maptools)

path.ch <- getPathShp('CH', year = 2014)
mu <- readOGR(path.ch, layer = 'municipalities')

mu <- spTransform(mu, CRS("+init=epsg:4326"))
mu.df <- formatShp(mu)
gname <- unique(mu.df$GEMNAME)

sum(!gname %in% data$loc)
sum(!unique(mu.df$BFSNR) %in% data$idn)
```